A numerical study of fixation probabilities for strategies in the Iterated Prisoner's Dilemma

### 2017-04-12 tex/main.tex
Move Marc's notes to results section.
Fix abstract.
Draft the introduction section.
Have included an image of the Moran process.

% Packages
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{xstring}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}

@@

\begin{itemize}
    \item Overview of Moran processes;
    \item Review of the literature (\cite{Lee2015, Nowak, Moran1957});
    \item Short discussion about the Axelrod library.
\end{itemize}

Some work has looked at evolutionary stability of strategies within the
Prisoner's Dilemma \cite{Li2014} but this is not done in the more widely used
setting of the Moran process but in terms of infinite population stability.

In \cite{Baek2016} Moran processes are looked at in a theoretic framework for a
small subset of strategies.

In \cite{Lee2015} machine learning techniques are used to train a strategy
capable of resisting invasion and also invade any memory one strategy.

@@

Note that due to the high computational cost of these experiments, for any given
interaction between two players within the Moran process the outcome is sampled
from a pre computed cache of 10000 match outcomes. This is carried out using the
approximate Moran process implemented in \cite{axelrodproject}.

As an example, Figure~\ref{fig:players_with_most_scores} shows the scores
between two players that over the 10000 outcomes gives 6817 different scores.

@@

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Cooperator_1000_repetitions.pdf}
        \caption{Alternator and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Defector_1000_repetitions.pdf}
        \caption{Alternator and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Tit_For_Tat_1000_repetitions.pdf}
        \caption{Alternator and Tit For Tat}
    \end{subfigure}%

>>>>

% Packages
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{xstring}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{standalone}

\usepackage{tikz}
\usetikzlibrary{calc, shapes}

@@

Figure~\ref{fig:moran_process} shows a diagrammatic representation of the Moran
process. The Moran process is a stochastic birth death process on a finite
population in which the population size stays constant over time. Individuals
are \textbf{selected} according to a given fitness landscape. Once selected, a
given individual is reproduced and similarly another individual is chosen to be
removed from the population. In some settings mutation is also considered but
without mutation (the case considered in this work) this process will arrive at
an absorbing state where the population is entirely made up of a single
individual. The probability with which a given strategy is the survivor is call
the absorption probability. A more detailed analytic description of this is
given in Section~\ref{sec:validation}.

\begin{figure}[!hbtp]
    \centering
    \input{../img/moran_process.tex}
    \label{fig:moran_process}
    \caption{A diagrammatic representation of a Moran process}
\end{figure}

The Moran process was initially introduced in \cite{Moran1957} in a genetic
setting. It has sine been used in a variety of settings including the
understanding of the spread of cooperative behaviour. However, as stated before,
these mainly consider non sophisticated strategies. Some work has looked at
evolutionary stability of strategies within the Prisoner's Dilemma \cite{Li2014}
but this is not done in the more widely used setting of the Moran process but in
terms of infinite population stability. In \cite{Baek2016} Moran processes are
looked at in a theoretic framework for a small subset of strategies. In
\cite{Lee2015} machine learning techniques are used to train a strategy capable
of resisting invasion and also invade any memory one strategy.
% TODO Is this OK? We should add more.

The contribution of this work is a detailed and extensive analysis of absorption
probabilities for 172 strategies. These strategies and the numerical simulations
are from~\cite{axelrodproject} which is an open source research library written
for the study of the IPD. The strategies and simulation frameworks are
automatically tested in accordance to best practice. The large number of
strategies are available thanks to the open source nature of the project with
over 40 contributions made by different programmers.

Section~\ref{sec:methodology} will explain the methodological approach used,
Section~\ref{sec:validation} will validate the methodology by comparing
simulated results to analytical results. The main results of this manuscript are
presented in Section~\ref{sec:numerical_results} which will present a detailed
analysis of all the data generated. Finally, Section~\ref{sec:conclusion} will
conclude and offer future avenues for the work presented here.

@@

Note that due to the high computational cost of these experiments, for any given
interaction between two players within the Moran process the outcome is sampled
from a pre computed cache of 1000 match outcomes. This is carried out using the
approximate Moran process implemented in \cite{axelrodproject}.

As an example, Figure~\ref{fig:players_with_most_scores} shows the scores
between two players that over the 1000 outcomes gives 971 different scores.

@@

% TODO Cite all relevant pieces of software: pandas, matplotlib, scipy, axelrod
% etc...

% TODO Introduce the next section.

@@

% TODO Include more of these when finished.
\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Cooperator_1000_repetitions.pdf}
        \caption{Alternator and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Defector_1000_repetitions.pdf}
        \caption{Alternator and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Tit_For_Tat_1000_repetitions.pdf}
        \caption{Alternator and Tit For Tat}
    \end{subfigure}%
